Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-05 Response/Response 3/response-3.tex

\reviewF{The authors have modified the manuscript taken into account the reviewers' comments. However, the proof of convergence still lacks of convincing argumentation to make this paper suitable for publication. Two main aspects are arguable as follows: }

\vspace{1eM}
\underline{\textit{Reply:}} We thank the reviewer for all constructive comments. We agree with the reviewer's concern on the claim that convergence proof still lacks the convincing arguments. We have completely rewritten Appendix A-D with similar kind of arguments used to discuss the convergence of projected gradient algorithms in Nonlinear Programming book as suggested by the reviewer. We hope that the proposed changes would make the convergence proof complete.

\begin{itemize}

	\item \reviewF{When discussing the convergence of the SCA algorithm (Appendix A-C), the authors claim that the SCA algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

	\vspace{1eM}	
	\underline{\textit{Reply:}} We agree with the reviewer comment on the convergence of the sequence of beamformer iterates generated by the SCA algorithm. It is true that since the objective sequence is strictly monotonic and the minimizer is unique in each iteration, it does not guarantee the convergence of the sequence of iterates. We have removed our earlier claim on the convergence of beamformer iterates generated by the SCA algorithm. We now refer the minimizer obtained upon objective convergence is \eqn{\mbf{z}_\ast^{(i)}}, as presented in the paragraph following (51). Now, considering the whole sequence of beamformer iterates generated by repeatedly performing SCA and AO until the objective convergence, we can only show that the limit point of every convergent subsequence of iterates is a stationary point.

	We have revised our convergence of beamformer iterates in Appendix A-D using subsequence convergence proof. In order to do so, the feasible set should be compact. Even though the original set \eqn{\mc{F}} of nonconvex problem is compact, the feasible sets \eqn{\mc{X}^{(i)}_k} and \eqn{\mc{Y}^{(i)}_k} of relaxed subproblems need not be compact on all scenarios due to the newly introduced optimization variable \eqn{\beta_{l,k,n}} to bound the interference. It happens when \eqn{\gamma_{l,k,n} \to 0}, \textit{i.e.}, when the \eqn{\ith{k}} user stream \eqn{l} is not active on sub-channel \eqn{n}. In such a case, \eqn{\beta_{l,k,n}} can take any value, since \eqn{\gamma_{l,k,n} \to 0} as  \eqn{\mvec{m}{l,k,n} \to 0} and \eqn{\mvec{w}{l,k,n} \to 0}. It has no impact on the solution of each convex subproblem even if \eqn{\beta_{l,k,n} \to \infty}. However to discuss the convergence of proposed iterative algorithms, the feasible set needs to be compact.

	Therefore, we include an additional constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} without altering the problem or solution for the sake of convergence analysis. Note that \eqn{\beta_{l,k,n}} can be bounded above with \eqn{P_{\max}}, since the total interference power on each stream cannot exceed the total transmit power, which follows from the passive behavior of wireless channels. Using this additional constraint, the feasible set of each subproblem is guaranteed to be compact, and therefore the sequence of iterates generated by the iterative algorithm is bounded. This information is included in the paragraph after (28) on page 6.

	Furthermore, the convergence discussions on the sequence of iterates generated by the iterative algorithm is presented in Appendix A-D.

	\vspace{1eM}	
	\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{x} are updated simultaneously, based on \eqn{x^t}. But in the authors' model, the update of \eqn{x} is performed in two phases: in the first phase, only the elements of \eqn{m} and \eqn{\gamma} in \eqn{x} are updated based on \eqn{x^t}. In the second phase, the remaining elements of \eqn{x} are updated, i.e. \eqn{w} and \eqn{\gamma}, based on both \eqn{x^t} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

	\vspace{1eM}
	\underline{\textit{Reply:}} We agree with the reviewer's concern on lack of relevant references to show that the proposed method of alternating optimization variables can be applicable to the Zangwill's model. In [R1, Appendix I], the convergence of the sequence of iterates generated by the alternating projections algorithm was discussed with Zangwill's model using composition of two subalgorithms. However, based on reviewer's suggestion, we have modified the convergence proof similar to the one provided for gradient projection method in Nonlinear programming book by Bertsekas.

	In our earlier manuscript, the convergence of the sequence of beamformer iterates claim based on the Meyer's paper was incomplete. We apologize for the incomplete usage of the theorem presented in Meyer's paper [R2]. In [R2, Theorem. 3.1], it has been shown that if strict monotonicity of the objective sequence is guaranteed and the sequence of iterates is bounded, then either the sequence of beamformer iterates converges or the accumulation points of \eqn{\{x^t\}} is a continuum. Therefore, our earlier claim on the guaranteed convergence of the sequence of iterates is not correct as pointed out by the reviewer. The current approach of ensuring strict monotonic decrease in the objective sequence by using a quadratic regularization term in the objective as in projected gradient is discussed in [R2, Section 4] and in [R2, Lemma 4.1].

	\begin{itemize}
		\item[R1]  J. Tropp, I. Dhillon, R. Heath, and T. Strohmer, ``Designing structured tight frames via an alternating projection method," \emph{IEEE Trans. Inform. Theory}, vol. 51, no. 1, pp. 188–209, Jan. 2005.
		\item[R2] R.R. Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol. 12, no. 1, pp. 108-121, 1976
	\end{itemize}

\end{itemize}

### 2015-11-05 Report/convergence_centralized.tex
updated discussion

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

>>>>

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

### 2015-11-05 Report/convergence_distributed.tex
updated discussion

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence. Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \rightarrow \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.

To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}

@@

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}. The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size. It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.

To prove the convergence of the \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
\begin{subeqnarray}
	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \slabel{const-admm} \\
&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2 \eqsub
\end{subeqnarray}
the following conditions are required for the convergence.
\begin{itemize} \allowdisplaybreaks
	\item \me{G,H} should be convex
	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
\end{itemize}
Note that the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible. The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior. The feasibility of the interior point is verified by having a non-zero precoder for only one user. Therefore, by following \cite[Prop. 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}. The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.

>>>>

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence. Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \to \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.

To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \to \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions presented in Appendix \ref{sec-3.5}.}

@@

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}. The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \to \infty} \cite{bertsekas1999nonlinear} for a diminishing step size. It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.

To prove the convergence of the \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
\begin{subeqnarray}
	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \slabel{const-admm} \\
&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2 \eqsub
\end{subeqnarray}
the following conditions are required for the convergence.
\begin{itemize} \allowdisplaybreaks
	\item \me{G,H} should be convex
	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
\end{itemize}
Note that the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible. The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior. The feasibility of the interior point is verified by having a non-zero precoder for only one user. Therefore, by following \cite[Prop. 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \to \infty}. The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.

### 2015-11-05 Report/kkt_mse_approach.tex
updated stationarity
updated discussion

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of complete \ac{CSI} at the transmitter. Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized}. Since the work in \cite{kaleva2013decentralized} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints. However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables. In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the problem, namely,
\begin{itemize}
\item when the exponent \me{q} is even, or
\item when the number of backlogged packets waiting to be transmitted for each user is large enough, \textit{i.e}, \me{\textstyle Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator in the objective and queues in the first place as well.
\end{itemize}

With the assumption that either one of the above conditions, the problem in \eqref{eqn-mse-2} can be written as
\allowdisplaybreaks\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}\; \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1} \neqsub
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

>>>>

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of local \ac{CSI} at the transmitter that includes channel between \ac{BS} \eqn{b} and all interfering users in the system. Similar work has been considered for the \ac{WSRM} problem with minimum guaranteed rate constraints in \cite{kaleva2013decentralized}. Since the work in \cite{kaleva2013decentralized} is similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint as in \eqref{eqn-3.1.4}, the formulation in \cite{kaleva2013decentralized} require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

However, in the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints. However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables. In order to make the objective function differentiable, we consider the following two conditions in which the absolute operator can be ignored without affecting the problem, namely,
\begin{itemize}
\item when the exponent \me{q} is even, or
\item when the number of backlogged packets waiting to be transmitted for each user is large enough, \textit{i.e}, \me{\textstyle Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator in the objective and queues in the first place as well.
\end{itemize}

Assuming that either one of the above conditions is satisfied, the problem in \eqref{eqn-mse-2} can be written as
\allowdisplaybreaks\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}\; \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1} \neqsub
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
